---
title: Class Script
subtitle: "UL"
author:
  - name: Byeong-Hak Choe
    
date: 2026-04-27

execute: 
  echo: true
  eval: true
  warning: false
  message: false
  fig-width: 10
  fig-height: 6

format:
  html:
    code-fold: false
    toc: true
    toc-title: "Contents"
    toc-expand: 3
    number-sections: true
    code-tools: true
    highlight-style: atom-one
---


```{r}
library(arules)

tmp <- tempfile(fileext = ".tsv.gz")
download.file("https://bcdanl.github.io/data/bookdata.tsv.gz",
              destfile = tmp, mode = "wb", quiet = TRUE)

bookbaskets <- read.transactions(
  tmp,
  format        = "single",
  header        = TRUE,
  sep           = "\t",
  cols          = c("userid", "title"),
  rm.duplicates = TRUE
)
```


```{r}
class(bookbaskets)
dim(bookbaskets)

colnames(bookbaskets)[1:5]
rownames(bookbaskets)[1:5]
```



```{r}
basketSizes <- size(bookbaskets)
summary(basketSizes)

quantile(basketSizes, probs = seq(0, 1, 0.1))

basketSizes_df <- data.frame(count = basketSizes)

library(tidyverse)
ggplot(basketSizes_df) +
  # geom_density(aes(x = count)) +
  geom_histogram(aes(x = count)) +
  scale_x_log10() +
  labs(title = "Distribution of Basket Sizes (log scale)", x = "Basket size", y = "Density")
```


```{r}
bookCount    <- itemFrequency(bookbaskets, "absolute")

bookCount

bookCount_df <- data.frame(
  item = names(bookCount),
  n = bookCount,
  row.names = NULL
)

bookCount_df <- bookCount_df |> 
  arrange(-n) |> # popular books 
  # Fraction of transactions containing the most popular book
  mutate(pct = n / nrow(bookbaskets))
```



```{r}
# Restrict to customers who expressed interest in at least 2 books
bookbaskets_use <- bookbaskets[size(bookbaskets) > 1]
dim(bookbaskets_use)
dim(bookbaskets)

rules <- apriori(
  bookbaskets_use,
  parameter = list(support = 0.002, confidence = 0.75)
)


```



```{r}
summary(rules)
```



```{r}
measures <- interestMeasure(
  rules,
  measure      = c("coverage", "fishersExactTest"),
  transactions = bookbaskets_use
)
summary(measures)
```
```{r}
rules |>
  sort(by = "confidence") |>
  head(n = 5) |>
  inspect()
```

```{r}
top5_rules <- rules |>
  sort(by = "confidence") |>
  head(n = 5) |>
  as("data.frame")
```


```{r}
library(arulesViz)

# Scatter plot: support vs. confidence, shaded by lift
plot(rules,
     method  = "scatterplot",
     measure  = c("support", "confidence"),
     shading  = "lift",
     engine   = "ggplot2")
```

```{r}
plot(rules, method = "graph",  engine = "htmlwidget")

```



```{r}
#| fig-width: 10
#| fig-height: 10
# Graph plot: items as nodes, rules as edges
# Subset to top 20 rules by lift for readability
rules |>
  sort(by = "lift") |>
  head(n = 20) |>
  plot(method  = "graph",
       engine  = "ggplot2")
```

```{r}
# Grouped matrix: LHS groups vs. RHS items
plot(rules,
     method  = "grouped matrix",
     engine  = "ggplot2") +
  coord_flip()
```
```{r}
brules <- apriori(
  bookbaskets_use,
  parameter  = list(support = 0.001, 
                    confidence = 0.6),
  appearance = list(rhs = c("The Lovely Bones: A Novel"),
                    default = "lhs")
)

summary(brules)

brules |>
  sort(by = "confidence") |>
  lhs() |>
  head(n = 5) |>
  inspect()


plot(rules, 
     method = "graph",  
     engine = "htmlwidget")


plot(brules, 
     method = "graph",  
     engine = "htmlwidget")




```


```{r}
library(tidyverse)
library(rmarkdown)

library(arules)
library(arulesViz)
library(plotly)
```

```{r}
path_music <- "https://bcdanl.github.io/data/music_old.tsv"

music_eg <- read.transactions(
  file = path_music,
  format = "single",
  header = TRUE,
  cols = c(1, 2),
  rm.duplicates = TRUE
)
```


# Q1
What do the labels for the column and the row of music_eg represent?


```{r}
colnames(music_eg)[1:10]
rownames(music_eg)[1:5]
```

## Q2a
What are the first quartile, the median, the third quartile, and the maximum of transaction sizes in music_eg?


```{r}
musicSizes <- size(music_eg)
summary(music_eg)

quantile(musicSizes, probs = seq(0, 1, 0.1))

```



## Q2b
Visualize the distribution of transaction sizes.

```{r}

musicSizes_df <- data.frame(count = musicSizes)

ggplot(musicSizes_df) +
  geom_density(aes(x = count)) +
  # geom_histogram(aes(x = count)) +
  # scale_x_log10() +
  labs(title = "Distribution of Basket Sizes (log scale)", x = "Basket size", y = "Density")
```


## Q3a
Find the top 50 most frequently occurring items in music_eg.
Also find the top 50 least frequently occurring items in music_eg.

```{r}
musicCount    <- itemFrequency(music_eg, "absolute")

musicCount_df <- data.frame(
  item = names(musicCount),
  n = musicCount,
  row.names = NULL
)

musicCount_df <- musicCount_df |> 
  arrange(-n) |> # popular books 
  # Fraction of transactions containing the most popular book
  mutate(pct = n / nrow(music_eg))
```


## Q3b
Visualize the distribution of item occurrence.

```{r}
musicCount_df |> 
  head(10) |> 
  ggplot(aes(x = n,
             y = fct_reorder(item, n))) +
  geom_col()
```


## Q4

```{r}
basket_sizes <- size(music_eg)
musicbaskets_use <- music_eg[basket_sizes > 1]
```


## Q4a

From the subset of music_eg whose transaction size is greater than 1, find association rules with minimum support 0.01 and minimum confidence 0.5.


```{r}
# Restrict to customers who expressed interest in at least 2 books

dim(music_eg)
dim(musicbaskets_use)

mrules <- apriori(
  musicbaskets_use,
  parameter = list(support = 0.01, confidence = 0.5)
)
```

## Q4b

Pick one rule from Question 4a. Interpret the following qualities of the rule you pick:

support
confidence
coverage
lift
count

```{r}
summary(mrules)
```


## Q4c
Find at least 5 association rules for the item you pick by setting appropriate levels of minimum support and minimum confidence.



```{r}
mrules |>
  sort(by = "confidence") |>
  head(n = 5) |>
  inspect()
```

```{r}
mrules |>
  sort(by = "lift") |>
  head(n = 5) |>
  inspect()

```




