---
title: Linear Regression
subtitle: "DANL 320: Big Data Analytics"
author:
  - name: Byeong-Hak Choe
    
date: last-modified

execute: 
  echo: true
  eval: true
  warning: false
  message: false
  fig-width: 10
  fig-height: 6

format:
  html:
    code-fold: true
    toc: true
    toc-title: "Contents"
    toc-expand: 3
    number-sections: true
    code-tools: true
    highlight-style: atom-one
---

```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)
library(DT)
library(stargazer)
library(broom)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 90,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Essential Shortcuts

- Adding a code chunk
  - Mac: command + shift + I
  - Windows: Ctrl + Shift + I

- We write code within a code chunk  
```{r}

```

- To run entire lines of code within a code chunk
  - Mac: command + shift + return
  - Windows: Ctrl + Shift + Enter


- To run a current line of code within a code chunk
  - Mac: command + return
  - Windows: Ctrl + Enter


```{r}
library(tidyverse)
library(skimr)

```


# Linear Regression in R

```{r}
sale_df <- read_csv("https://bcdanl.github.io/data/home_sales_nyc.csv")
set.seed(123)   # for replication

sale_df <- sale_df |>
  mutate(gp = runif(n()))

dtrain <- sale_df |> filter(gp >= 0.4)  # ~60%
dtest  <- sale_df |> filter(gp <  0.4)  # ~40%

nrow(dtrain) / nrow(sale_df)
```



```{r}
colnames(sale_df)
m1 <- lm(sale_price ~ gross_square_feet,
         data = dtrain)
summary(m1)
```

```{r}
#| results: asis
stargazer(
  m1,
  type = "html",
  title = "Simple Linear Regression (Training Data)",
  dep.var.labels = "Sale Price"
)
```


```{r}
stargazer(
  m1,
  type = "text",
  title = "Simple Linear Regression (Training Data)",
  dep.var.labels = "Sale Price"
)
```

# Prediction

```{r}
dtest <- dtest |> 
  mutate(pred_m1 = predict(m1, newdata = dtest))

# Test RMSE
rmse_m1 <- dtest |> 
  mutate(resid_sq = (sale_price - pred_m1)^2) |> 
  summarize(
    rmse_m1 = mean(resid_sq)
    )
```


```{r}
df_pred <- augment(m1)  # broom::augment()
```



# Multivariate Linear Regression

```{r}
#| results: asis

m2 <- lm(sale_price ~ gross_square_feet + age, data = dtrain)

stargazer(
  m1, m2,
  type = "html",
  title = "Simple vs Multivariate Regression (Training Data)"
)
```


